---
title: "Quiz: tidyverse functions"
author: "By [Matt Dray](https://twitter.com/mattdray)"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE, context="setup"}
# Set chunk options
knitr::opts_chunk$set(echo = FALSE)

# Get packages
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(learnr))
suppressPackageStartupMessages(library(pacman))
suppressPackageStartupMessages(library(shiny))
suppressPackageStartupMessages(library(emo))

# Character vector of tidyverse package names
tidy_pkgs <-
  tidyverse::tidyverse_packages() %>%  # calls character vector
  str_replace("\n", "") %>%  # remove newline
  str_replace(">=", "") %>%  # remove greater than or equal to
  str_replace("[:punct:]", "")  # remove punctuation
  
# Install and load full set of tidyverse packages
pacman::p_load(
  char = tidy_pkgs,
  character.only = TRUE  # read elements of character vector, not object name
)

# Tibble where each row is a package-function combination
tidy_funs <-
  tidy_pkgs %>% 
  tibble::enframe(name = NULL, value = "package") %>% 
  dplyr::mutate(
    functions = purrr::map(
      package,
      ~pacman::p_functions(.x, character.only = TRUE)
    )
  ) %>% 
  tidyr::unnest()
```

<br>

`r emo::ji("information_source")` Can you select the correct package for the named tidyverse function? Made with [{learnr}](https://rstudio.github.io/learnr/), the [tidyverse](https://www.tidyverse.org/) and [{pacman}](https://cran.r-project.org/web/packages/pacman/index.html).

`r emo::ji("twisted_rightwards_arrows")` Generate a random question by setting a seed value and pressing 'Go'. Use this seed again to retrieve the same question.

`r emo::ji("new")` For a new question, click 'Start Over' in the menu pane, select a new seed value and hit 'Go'.

```{r, button, echo=FALSE}
# This chunk contains a Shiny action button
# Set a seed value to 'control the randomness' of sampling functions/packages
# Click the button to apply the value to set.seed()

numericInput("n", "Set seed:", value = 1337)
actionButton("goButton", "Go")
```

```{r, server, context="server"}
# This chunk attempts to builds the text output that can be passed later to the
# quiz() and answer() functions

# Get function name for subject of question
fun_name <- eventReactive(
  input$goButton,
  { 
    set.seed(input$n)
    fun_sample <- sample_n(tidy_funs, 1)
    fun_name <- select(fun_sample, functions) %>% pull()
    return(fun_name)
  }
)
output$fun_name_out <- renderText({
  paste0("The function `", fun_name(), "` is from which tidyverse package?")
})

# Get correct answer
ans_correct <- eventReactive(
  input$goButton,
  { 
    set.seed(input$n)
    fun_sample <- sample_n(tidy_funs, 1)
    ans_correct <- select(fun_sample, package) %>% pull()
    return(ans_correct)
  }
)
output$ans_correct_out <- renderText({ paste0("{", ans_correct(), "}") })

# Get wrong answer 1 of 3
ans_wrong1 <- eventReactive(
  input$goButton,
  { 
    set.seed(input$n)
    fun_sample <- sample_n(tidy_funs, 1)
    fun_name <- select(fun_sample, functions) %>% pull()
    dup_lookup <- tidy_funs %>% 
      filter(functions == fun_name) %>% 
      pull(package)
    ans_correct <- fun_sample %>% select(package) %>% pull()
    ans_wrong1 <- tidy_funs %>%
      distinct(package) %>%  # get unique packages
      filter(!package %in% c(dup_lookup)) %>%  # ignore packages containing function
      sample_n(1) %>%  # choose a remaining package name at random
      pull()  # to character
    return(ans_wrong1)
  }
)
output$ans_wrong1_out <- renderText({ paste0("{", ans_wrong1(), "}") })

# Get wrong answer 2 of 3
ans_wrong2 <- eventReactive(
  input$goButton,
  { 
    set.seed(input$n)
    fun_sample <- sample_n(tidy_funs, 1)
    fun_name <- select(fun_sample, functions) %>% pull()
    dup_lookup <- tidy_funs %>% 
      filter(functions == fun_name) %>% 
      pull(package)
    ans_correct <- fun_sample %>% select(package) %>% pull()
    ans_wrong1 <- tidy_funs %>%
      distinct(package) %>%
      filter(!package %in% c(dup_lookup, ans_wrong1)) %>% 
      sample_n(1) %>%
      pull()
    return(ans_wrong2)
  }
)
output$ans_wrong2_out <- renderText({ paste0("{", ans_wrong2(), "}") })

# Get wrong answer 3 of 3
ans_wrong3 <- eventReactive(
  input$goButton,
  { 
    set.seed(input$n)
    fun_sample <- sample_n(tidy_funs, 1)
    fun_name <- select(fun_sample, functions) %>% pull()
    dup_lookup <- tidy_funs %>% 
      filter(functions == fun_name) %>% 
      pull(package)
    ans_correct <- fun_sample %>% select(package) %>% pull()
    ans_wrong1 <- tidy_funs %>%
      distinct(package) %>%
      filter(!package %in% c(dup_lookup, ans_wrong1, ans_wrong2)) %>% 
      sample_n(1) %>%
      pull()
    return(ans_wrong3)
  }
)
output$ans_wrong3_out <- renderText({ paste0("{", ans_wrong3(), "}") })
```

```{r, q1}
quiz(
  caption = "Question ",
  question(
    text = as.character(textOutput("fun_name_out")),
    answer(as.character(textOutput("ans_correct_out")), correct = TRUE),
    answer(as.character(textOutput("ans_wrong1_out"))),
    answer(as.character(textOutput("ans_wrong2_out"))),
    answer(as.character(textOutput("ans_wrong3_out"))),
    random_answer_order = TRUE
  )
)
```
